### 2014-10-08 fundamentals/examples.tex
add more recycle scenario details. Added in some xml snippets

Simulations have been run in the past and more are being run. FCO is an 
example.

>>>>

\TODO{discuss FCO?}

Results of some simple recycle scenarios run in \Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass MOX recycle is
easy to implement.  The simulation initially included one provider of fresh
UOX fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation duration was set to 1100 months.

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources dilineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange makes it easy for a reactor to
preferrentially accept recycled MOX fuel over fresh UOX fuel.  The
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

\begin{lstlisting}[language=xml]
  ...
  <BatchReactor>
      ...
      <processtime>18</processtime>
      <nbatches>3</nbatches>
      <batchsize>20000</batchsize>
      <refueltime>2</refueltime>
      ...
  </BatchReactor>
  ...
\end{lstlisting}

The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flow-modopen}.

\begin{figure}[!]
\label{fig:flow-modopen}
\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

To switch to a fully closed fuel cycle, all that needs to be done is change
the output commodity for the \Class{BatchReactor}'s spent MOX fuel.  All this
requires is a one-word change in the input file:

\begin{lstlisting}[language=diff]
  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
  @@ -108,7 +108,7 @@
           <fuel>         
             <incommodity>mox_fuel</incommodity>
             <inrecipe>lwr_mox_fuel</inrecipe>
  -          <outcommodity>spent_mox</outcommodity>
  +          <outcommodity>spent_fuel</outcommodity>
             <outrecipe>mox_spent_fuel</outrecipe>
           </fuel>
\end{lstlisting}

This results in new the material flows in Figure \ref{fig:flow-closed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not very realistic for the full, multipass
recycle case.

\begin{figure}[!]
\label{fig:flow-closed}
\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

\TODO{discuss Pu buildup charts}

\begin{figure}[!]
\label{fig:puseries-1}
\caption{bla}
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\end{figure}

\begin{figure}[!]
\label{fig:puseries-n}
\caption{bla}
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\end{figure}

### 2014-10-08 fundamentals/impl.tex
todo note
add more recycle scenario details. Added in some xml snippets

Although concept of the RIF hierarchy is provided, the \Cyclus kernel is
really designed to handle hierarchies of arbitrary depth.  It is just as easy
to run a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents' of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
to implement agents that deploy copies of themselves, or that schedule their
own decommissioning.  Because regions, institutions, and facilities are all
just agents, they can all be implemented to excersize the full set of features
offerred to by the \Cyclus kernel.

@@

    \item "lazy" (future) decays any material whenever its composition is
        viewed (e.g. when an agent queries information about a material's
        $^{239}Pu$ content).

@@

In large simulations there may be many material objects changing frequently.
Material decay can also contribute significantly to such changes.  In order to
help avoid unnecessary runtime performance and database space impacts,
compositions in Cyclus have some special features.  Compositions in Cyclus are
immutable.  This immutability allows multiple material objects to all hold
references to the same composition object safely.  When operations are
performed on a material that don't change the composition, any new resulting
materials hold a reference to the same, originating composition object.
Although the decay operation generates a new, separate composition (preserving
immutability), a reference to the new composition is placed in a cache shared
by the new an originating compositions. The next time the originating
composition is decayed, this cache will be checked for a prior calculation
with the same cumulative decay time.  If one exists, the cached composition is
used.  This cache is shared by all compositions that transitively come from
the same origin.  Composition immutability in concert with decay history
caching help eliminate many redundant decay calculations in addition to
reducing the total number of composition objects.  Since each composition
object is only recorded in the database once, significant space savings also
occurs.

>>>>

Although concept of the RIF hierarchy is provided, the \Cyclus kernel is
really designed to handle hierarchies of arbitrary depth.  It is just as easy
to run a simulation without regions and institutions (i.e.  only facilities)
or a simulation having archetypes that are the parents' of regions.  By
convention, institutions are mainly responsible for facility deployment, but
any archetype can have access to \Cyclus' agent deployment mechanism.  It easy
to implement agents that deploy copies of themselves, or that schedule their
own decommissioning.  Because regions, institutions, and facilities are all
just agents, they can all be implemented to exercise the full set of features
offered by the \Cyclus kernel.

@@

    \item "lazy" (future) decays any material whenever its composition is
        viewed (e.g. when an agent queries information about a material's
        $^{239}$Pu content).

@@

In large simulations there may be many material objects changing frequently.
Material decay can also contribute significantly to such changes.  In order to
help avoid unnecessary runtime performance and database space impacts,
compositions in Cyclus have some special features.  Compositions in Cyclus are
immutable.  This immutability allows multiple material objects to all hold
references to the same composition object safely.  When operations are
performed on a material that don't change the composition, any new resulting
materials hold a reference to the same, originating composition object.
Although the decay operation generates a new, separate composition (preserving
immutability), a reference to the new composition is placed in a cache shared
by the new an originating compositions. The next time the originating
composition is decayed, this cache will be checked for a prior calculation
with the same cumulative decay time.  If one exists, the cached composition is
used.  This cache is shared by all compositions that transitively come from
the same origin.  Composition immutability in concert with decay history
caching help eliminate many redundant decay calculations in addition to
reducing the total number of composition objects.  Since each composition
object is only recorded in the database once, significant space savings also
occurs. \TODO{do we want a diagram helping show this composition caching?}
